Modelling last glacial cycle ice dynamics in the Alps

### 2017-09-15 articles/cycle/alps-cycle.tex
Add references on ice extent.

>>>>

    The LGM extent of alpine glaciers has been mapped with varying level of
    across the mountain range \citep{Penck.Bruckner.1909, Jackli.1962,
    Bini.etal.2009, Coutterand.2010, Bavec.Verbic.2011,
    Buoncristiani.Campy.2011, Husen.2011}. These maps have been compiled
    into an reconstruction covering the entire Alps \citep{Ehlers.etal.2011},
    reproduced here (Fig.~4, red line) for comparison against model results.
